---
title: "JOINING DATASETS"
author: "Grace Abels"
date: "2/15/2022"
output: pdf_document
editor_options: 
  chunk_output_type: console
---
JOINING DATASETS
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(knitr)
```

```{r load data, warning=FALSE, message= FALSE}
pf_final <- read_csv("pf_final.csv")
tagged_claims <- read_csv("tagged_claims_for_join.csv")
```

```{r join data}
full_data <- pf_final %>%
  left_join(tagged_claims, by = c("text" = "text",
                                  "title" = "title",
                                  "claimant_party" = "claimant_party",
                                  "url" = "url",
                                  "textualRating" = "textualRating",
                                  "ratingsimp" = "ratingsimp",
                                  "T/F RQ1" = "T/F RQ1",
                                  "claimant_canonical_name" = 
                                    "claimant_canonical_name"))

```

```{r narrow to relevant variables}
#narrowed_full_data <- full_data %>%
  #select(url, title, reviewDate, text, claimDate, claimant_canonical_name, claimant_party, textualRating, `T/F RQ1`, #claimYear:`Media and Communications`)
```
```{r}
clean_full_data <- full_data %>%
  mutate(textualRating = case_when(textualRating == "TRUE" ~ "True", 
                   textualRating == "FALSE" ~"False", 
                   textualRating == "Mostly True" ~ "Mostly True", 
                   textualRating == "Half True" ~ "Half True", 
                   textualRating == "Mostly False" ~ "Mostly False", 
                   textualRating == "Pants on Fire" ~ "Pants on Fire"))
clean_full_data$textualRating <- factor(clean_full_data$textualRating,
                                 levels = c("True", 
                                            "Mostly True", 
                                            "Half True", 
                                            "Mostly False", 
                                            "False", 
                                            "Pants on Fire"))
```

```{r}
write.csv(clean_full_data, 'TF_tagged_PF.csv', row.names = FALSE)
```


``` {r rating by party,  warning=FALSE, message= FALSE}
#ggplot(clean_full_data, aes(x = textualRating, fill = claimant_party)) + 
 #geom_bar(position = "fill") + 
  #scale_fill_manual( values = c("blue2", "red3")) + 
  #labs(title = "Ratings level by Party",
       #x = "Rating", 
       #y = "Proportion", 
       #fill = "Party of claimant")
```

```{r}

```

{r party by rating,  warning=FALSE, message= FALSE}
ggplot(pf_final, aes(x = claimant_party, fill = textualRating)) + 
         geom_bar(position = "fill") + 
  scale_fill_manual( values = c("#1a9850",
                                "#91cf60",
                                "#d9ef8b", 
                                "#fee08b", 
                                "#fc8d59", 
                                "#d73027")) +
  labs(title = "Percentage Rating by Party", 
       x = "Claims by Party", 
       fill = "Rating", y = "Percentage" )


{r table,  warning=FALSE, message= FALSE}
pf_final %>%
  count(claimant_party, textualRating) %>%
  pivot_wider(id_cols = c(claimant_party, 
                          textualRating),
              names_from = textualRating,
              values_from = n,
              values_fill = 0) %>% 
  kable()


